\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}                    
\usepackage[scale=0.75]{geometry}
\usepackage{import}

\name{Jashwanth}{Gowda R}
\email{webdevjash6@gmail.com}
\homepage{jashwanthgowda.netlify.app}
\phone[mobile]{+91-9986621042}
\social[linkedin]{jashwanthgowda-6666}
\social[github]{Jashwanth-Gowda-R}

\begin{document}

\makecvtitle

\vspace{3pt}

\section{Summary}

Experienced Software Engineer with over 4 years of overall development experience, specializing in both mobile and web applications. Demonstrated 3+ years of expertise in Flutter for building cross-platform mobile apps (Android, iOS) and strong experience in ReactJS for modern web development. Proficient in Dart, JavaScript, Firebase, RESTful APIs, and state management solutions like Riverpod and Stacked. Adept at working in Agile teams, following clean architecture principles (MVVM), and delivering high-performance, scalable applications. Skilled in CI/CD automation, app deployment (Play Store, App Store), and performance optimization. Passionate about open-source contributions, UI/UX design, and continuous learning. Currently contributing to the global expansion of a mobile platform at ProWork.ie.

\section{Education}
\begin{itemize}
\item \cventry{2015 - 2019}{\textbf{Undergraduate}}{Don Bosco Institute Of Technology, VTU}{Bengaluru, India}{\textbf{Bachelor of Telecommunication Engineering}}{}
\end{itemize}

\section{Experience}
\subsection{Full-time Employment}

\item \cventry{Dec.2023 - Present}{\textbf{Flutter Developer}}{\href{https://www.prowork.ie/}{ProWork}}{Remote}{}
{
\begin{itemize}
    \item Developed a new cross-platform mobile application to expand ProWork’s global presence.
    \item Wrote scalable Flutter code following MVVM architecture and modular principles.
    \item Integrated Firebase services (Auth, Firestore, Storage) and REST APIs.
    \item Collaborated with UI/UX teams to implement responsive designs.
    \item Handled full deployment lifecycle on Play Store and App Store.
    \item Set up CI/CD workflows using GitHub Actions for automated builds.
    \item Performed code reviews and optimized app performance.
\end{itemize}
}

\item \cventry{Jul.2021 - Nov.2022}{\textbf{Software Engineer I}}{\href{https://www.digitalgreen.org/}{Digital Green}}{Bengaluru, India}{}
{
\begin{itemize}
    \item Developed a Flutter app to assist agricultural workers with crop data collection.
    \item Co-built a \href{https://farmstack.co/}{data sharing platform} in ReactJS.
    \item Created a \href{https://dashboard.digitalgreen.org/}{PowerBI dashboard} for in-house data visualization.
\end{itemize}
}

\item \cventry{Oct.2019 – Apr.2021}{\textbf{Software Engineer}}{\href{https://vrook.co/}{Vrook}}{Bengaluru, India}{}
{
\begin{itemize}
    \item Built mobile-responsive OpenEdX LMS themes.
    \item Added features for booksbeka.com using OpenCart.
    \item Created a company blog using GhostJS.
\end{itemize}
}

\subsection{Internships}

\item \cventry{Feb. 2019 – Apr. 2019}{\textbf{Bachelor Project}}{\href{https://www.isro.gov.in/}{ISRO}}{Bengaluru, India}{}
{
\begin{itemize}
    \item Designed a 1KV DC Rectifier Unit for Doppler Weather Radar.
    \item Worked on power supply systems with the radar design team.
\end{itemize}
}

\subsection{Freelancing}

\item \cventry{Apr.2023 – Jul.2023}{\textbf{Flutter Developer}}{\href{https://imcls.org/}{IMCLS}}{Remote}{}
{
\begin{itemize}
    \item Developed a storybook reader app for the \href{https://en.wikipedia.org/wiki/Idu_Mishmi_language}{Idu Mishmi} language.
\end{itemize}
}

\item \cventry{Sep.2021 – Nov.2021}{\textbf{Data Curator}}{\href{https://xri.institute/}{XRI Institute}}{Remote}{}
{
\begin{itemize}
    \item Created stakeholder network data for low-resource languages.
\end{itemize}
}

\item \cventry{Aug.2020 – Oct.2020}{\textbf{Frontend Developer}}{\href{https://foodveda.in/}{Foodveda}}{Remote}{}
{
\begin{itemize}
    \item Developed an OpenCart e-commerce platform for Indian food products.
\end{itemize}
}

\item \cventry{Jun.2020 – Jul.2020}{\textbf{Frontend Developer}}{NammaLocal}{Remote}{}
{
\begin{itemize}
    \item Created an OpenCart-based e-commerce site for local sellers.
\end{itemize}
}

\subsection{Personal Projects}

\item \cventry{}{Flutter Developer}{\href{https://play.google.com/store/apps/details?id=imcls.dictionary.demo_flutter}{Mishmi (Idu) Dictionary}}{Remote}{}
{
\begin{itemize}
    \item Added UI and audio features to an offline Flutter-based dictionary app.
\end{itemize}
}

\item \cventry{}{Frontend Developer}{\href{https://projectvani.org/about/}{VANI Project}}{Remote}{}
{
\begin{itemize}
    \item Customized responsive themes using Jekyll for a static archive website.
\end{itemize}
}

\section{Skills}
\begin{itemize}
    \item \textbf{Languages & Frameworks:} Dart, JavaScript, Flutter, ReactJS, Riverpod, Stacked, Bootstrap, Jekyll
    \item \textbf{Mobile/Web Technologies:} Firebase (Auth, Firestore, Storage), Appwrite, REST APIs, OpenCart, PowerBI
    \item \textbf{Tools & Practices:} Git, Jira, Agile/Scrum, Clean Architecture, CI/CD (GitHub Actions), Unit Testing
    \item \textbf{Databases:} Firestore, MySQL, SQLite, Drift
    \item \textbf{Deployment & DevOps:} Docker, AWS, Netlify, Vercel, Play Store, App Store
\end{itemize}

\section{Certifications}
\begin{itemize}
    \item \href{https://drive.google.com/file/d/1_ucRipd-6IVOl7d7c_RrxXeFLhvNtAYg/view?usp=sharing}{Flutter Foundations Course - Complete Package} by Andrea Bizzotto, Dec 2022
    \item \href{https://drive.google.com/file/d/1zp7iSDNFgM1W0UPfpp50O1DM91jSRnw0/view?usp=sharing}{The Complete Dart Language Guide for Beginners and Beyond} by Andrea Bizzotto, June 2022
\end{itemize}

\end{document}
