\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}                    
\usepackage[scale=0.75]{geometry}
\usepackage{import}

\name{Jashwanth}{Gowda R \break}
\email{webdevjash6@gmail.com}   
\homepage{jashwanthgowda.netlify.app}
% \photo[64pt][0.4pt]{images/image.png}
% \address{street and number}{postcode city}{country}
\phone[mobile]{+91-9986621042}
\social[linkedin]{jashwanthgowda-6666}
\social[github]{Jashwanth-Gowda-R}


\begin{document}

\makecvtitle

\vspace{3pt}
I am an experienced Flutter software developer with 3 years of industry expertise. I am proficient in building cross-platform applications and delivering user-centric solutions. 

\section{Education}

\vspace{3pt}

% \subsection{Academic Qualifications}

% \vspace{6pt}

\begin{itemize}

\item{\cventry{2015 - 2019}{\textbf{Undergraduate}}{Don Bosco Institute Of Technology, VTU}{Bengaluru, India}{\textbf{Bachelor of Telecommunication Engineering}}{}}

\end{itemize}

\vspace{3pt}

\section{Experience}

\vspace{3pt}

\subsection{Full-time Employment}

\vspace{6pt}

\begin{itemize}

\item{\cventry{Jul.2021 - Nov.2022}{\textbf{Software Engineer I}}{\href{https://www.digitalgreen.org/}{Digital Green
} }{Bengaluru,India}{}{}}

\begin{itemize}
    \item Developed a mobile application using Flutter that enabled frontline agricultural workers to gather crop harvest data. This application aided Farmer Production Organizations (FPOs) in informed sales planning, analyzing crop trends, managing supply and demand, and linking FPOs with potential buyers.
    
    \item Involved in developing a {\href{https://farmstack.co/}{\underline {data platform}}} using ReactJS (with a team of 3) for enabling direct data sharing between organizations to prevent unintentional data misuse.  

    \item Designed and developed a web-based {\href{https://dashboard.digitalgreen.org/}{\underline {visualization dashboard}}} using ReactJS and PowerBI for visualizing the data aggregated from in-house app.
    
\end{itemize}


\vspace{6pt}



\item{\cventry{Oct.2019 – Apr.2021}{\textbf{Software Engineer}}{\href{https://vrook.co/}{Vrook} }{Bengaluru, India}{}{}}

\begin{itemize}
    \item Designed and developed custom mobile-responsive themes for {\href{https://openedx.org/}{\underline {OpenEdX}}} LMS.
    
    \item Implemented new features for booksbeka.com using {\href{https://www.opencart.com/}{\underline {OpenCart}}}.
    
    \item Designed and developed the company’s blogsite using {\href{https://ghost.org/}{\underline {GhostJS}}}.

\end{itemize}

\vspace{6pt}

\vspace{6pt}



\subsection{Internships}

\begin{itemize}

\vspace{6pt}

\item{\cventry{Feb. 2019 – Apr. 2019}{\textbf{Bachelor Project}}{\href{https://www.isro.gov.in/}{Department of Space, Indian Space Research Organisation (ISRO)}}{Bengaluru, India}{}{}}

\begin{itemize}
    \item Bachelor Project: Design of 1KV DC Rectifier Unit for S-Band pulsed HV transmitted in the field of Doppler Weather Radar. 

    \item Worked with the design team of the Doppler Weather Radar power supply team.

\end{itemize}

\vspace{6pt}


\end{itemize}

\vspace{6pt}


\vspace{6pt}

\subsection{Freelancing}

\begin{itemize}

\vspace{6pt}

\item{\cventry{Apr.2023 – Jul.2023}{\textbf{Flutter Developer}}{\href{https://imcls.org/}{Idu Mishmi Cultural Society (IMCLS)}}{Remote}{}{}}

\begin{itemize}
    \item Building a storybook e-reader application for the {\href{https://en.wikipedia.org/wiki/Idu_Mishmi_language}{\underline {Idu Mishmi}}} language. 

\end{itemize}
\vspace{6pt}
\item{\cventry{Sep.2021 – Nov.2021}{\textbf{Data Curator}}{\href{https://xri.institute/}{XRI Institute}}{Remote}{}{}}

\begin{itemize}
    \item Worked as a data curator and data annotator for creating a stakeholder network for low-resource languages.

\end{itemize}

\vspace{6pt}
\item{\cventry{Aug.2020 – Oct.2020}{\textbf{Frontend Developer}}{\href{https://foodveda.in/}{Foodveda}}{Remote}{}{}}

\begin{itemize}
    \item Designed and developed an e-commerce web application using {\href{https://www.opencart.com/}{\underline {OpenCart}}} that serves indigenous recipes and food products across India.

\end{itemize}

\vspace{6pt}
\item{\cventry{Jun.2020 – Jul.2020}{\textbf{Frontend Developer}}{\href{}{NammaLocal}}{Remote}{}{}}

\begin{itemize}
    \item Designed and developed an e-commerce web application using {\href{https://www.opencart.com/}{\underline {OpenCart}}} that provides a platform for local sellers to showcase their products.

\end{itemize}

\end{itemize}

\vspace{6pt}

\subsection{Personal Projects}

\begin{itemize}

\vspace{6pt}

\item{\cventry{}{\textbf{Flutter Developer}}{\href{https://play.google.com/store/apps/details?id=imcls.dictionary.demo_flutter&hl=en_IN&gl=US
}{Mishmi (Idu) Dictionary}}{Remote}{}{}}

\begin{itemize}
    \item Contributed towards developing screens and adding audio features for the flutter-based offline mobile application. 


\end{itemize}

\vspace{6pt}

\item{\cventry{}{\textbf{Frontend Developer}}{\href{https://projectvani.org/about/}{Vernacular Archive of Northeast India - VANI}}{Remote}{}{}}

\begin{itemize}
    \item Involved in designing and developing responsive theme customization for the static website using {\href{https://jekyllrb.com/}{\underline {Jekyll}}}.

\end{itemize}

\vspace{6pt}


\end{itemize}


\section{Skills}

\vspace{3pt}

\begin{itemize}

\vspace{6pt}

\item \textbf{Languages, Frameworks And Cloud services:} JavaScript, Dart, Flutter, Riverpod, ReactJS, Bootstrap, OpenCart, Jekyll, Firebase, Appwrite
\vspace{3pt}


\item \textbf{Tools:} Git, Jira
\vspace{3pt}
\item {\textbf{Databases:}} Firestore, MySQL, Sqlite
\vspace{3pt}
\item \textbf{Infrastructures:} Docker, AWS, Netlify, Vercel
\vspace{3pt}
\vspace{6pt}

\end{itemize}

\vspace{6pt}






\section{Certifications}

\item{\href{https://drive.google.com/file/d/1_ucRipd-6IVOl7d7c_RrxXeFLhvNtAYg/view?usp=sharing}{\underline{Flutter Foundations Course - Complete Package}} by Andrea Bizzotto in Dec, 2022.
\vspace{3pt}
\item{\href{https://drive.google.com/file/d/1zp7iSDNFgM1W0UPfpp50O1DM91jSRnw0/view?usp=sharing}{\underline{The Complete Dart Language Guide for Beginners and Beyond }} by Andrea Bizzotto in June, 2022.

\vspace{6pt}


% \section{Languages}
% \item \textbf{Kannada - Mother tongue; English - Proficient} 
% \vspace{25pt}

% References are available upon request.                  


\end{document}