% \documentclass[11pt,a4paper,sans]{moderncv}
% \moderncvstyle{banking}
% \moderncvcolor{blue}

% \usepackage[utf8]{inputenc}
% \usepackage[scale=0.75]{geometry}
% \usepackage{hyperref}
% \usepackage{fontawesome5}

% % ===================== SPACING TUNING =====================
% \setlength{\hintscolumnwidth}{2.8cm}
% \AtBeginDocument{\recomputelengths}

% % ===================== PERSONAL INFO (ATS / METADATA) =====================
% \name{Jashwanth}{Gowda R}
% \email{webdevjash6@gmail.com}
% \homepage{jashwanthgowda.netlify.app}
% \phone[mobile]{+91-9986621042}
% \social[linkedin]{jashwanthgowda-6666}
% \social[github]{Jashwanth-Gowda-R}

% % ===================== FIXED 70 / 30 HEADER =====================
% \renewcommand*{\makecvtitle}{%
% \noindent
% \begin{tabular}{@{}p{0.70\textwidth} p{0.30\textwidth}@{}}

% % -------- LEFT --------
% {\LARGE\bfseries Jashwanth Gowda R\\[-2pt]
%  \normalsize Flutter Developer}

% &

% % -------- RIGHT --------
% {\raggedleft\small
% \faEnvelope\ \href{mailto:webdevjash6@gmail.com}{webdevjash6@gmail.com}\\
% \faMobile\ +91-9986621042\\
% \faGlobe\ \href{https://jashwanthgowda.netlify.app}{jashwanthgowda.netlify.app}\\
% \faLinkedin\ \href{https://www.linkedin.com/in/jashwanthgowda-6666}{jashwanthgowda-6666}\\
% \faGithub\ \href{https://github.com/Jashwanth-Gowda-R}{Jashwanth-Gowda-R}
% }

% \end{tabular}
% \vspace{0.5em}
% \hrule
% \vspace{1em}
% }

% \begin{document}

% \makecvtitle

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}                    
\usepackage[scale=0.75]{geometry}
\usepackage{import}

\name{Jashwanth}{Gowda R}
\email{webdevjash6@gmail.com}
\homepage{jashwanthgowda.netlify.app}
\phone[mobile]{+91-9986621042}
\social[linkedin]{jashwanthgowda-6666}
\social[github]{Jashwanth-Gowda-R}

\begin{document}

\makecvtitle

\vspace{3pt}

% ===================== SUMMARY =====================
\section{Summary}
Senior-level Flutter Developer with 4+ years of professional experience delivering production-grade mobile and web applications across multiple domains. Specialized in building scalable cross-platform applications using Flutter (Android, iOS) with strong foundations in Clean Architecture (MVVM), state management (Riverpod, Stacked), and performance optimization. Experienced in integrating Firebase and RESTful APIs, setting up CI/CD pipelines, and managing end-to-end app releases on the Play Store and App Store. Proven ability to collaborate with cross-functional teams in Agile environments and deliver reliable, user-focused solutions. Currently contributing to the global rollout of a mobile platform at ProWork.ie.

% ===================== EDUCATION =====================
\section{Education}
\cventry{2015 -- 2019}{\textbf{Bachelor of Telecommunication Engineering}}{Don Bosco Institute of Technology, VTU}{Bengaluru, India}{}{}

% ===================== EXPERIENCE =====================
\section{Experience}

\cventry{Dec. 2023 -- Present}{\textbf{Flutter Developer}}{\href{https://www.prowork.ie/}{ProWork}}{Bengaluru, India}{}{
\begin{itemize}
    \item Contributing to the development and global rollout of a cross-platform Flutter application supporting ProWork’s international expansion.
    \item Designing and implementing scalable mobile features using Flutter and Dart, following Clean Architecture (MVVM) and modular design principles.
    \item Implementing robust state management using Riverpod to handle complex UI flows and asynchronous data.
    \item Integrating Firebase services (Authentication, Firestore, Cloud Storage) and RESTful APIs.
    \item Collaborating with product managers, designers, and QA engineers in Agile sprints.
    \item Managing the complete mobile release lifecycle for Play Store and App Store.
    \item Establishing CI/CD pipelines using GitHub Actions.
    \item Improving application performance through widget optimization and structured code reviews.
\end{itemize}
}

\cventry{Jul. 2021 -- Nov. 2022}{\textbf{Software Engineer I}}{\href{https://www.digitalgreen.org/}{Digital Green}}{Bengaluru, India}{}{
\begin{itemize}
    \item Developed and maintained a Flutter-based mobile application for agricultural data collection.
    \item Enabled Farmer Producer Organizations (FPOs) with analytics for sales planning.
    \item Co-built a ReactJS-based \href{https://farmstack.co/}{data-sharing platform}.
    \item Developed PowerBI dashboards for large-scale data visualization.
\end{itemize}
}

\cventry{Oct. 2019 -- Apr. 2021}{\textbf{Software Engineer}}{\href{https://vrook.co/}{Vrook}}{Bengaluru, India}{}{
\begin{itemize}
    \item Developed mobile-responsive OpenEdX LMS themes.
    \item Implemented OpenCart-based e-commerce features.
\end{itemize}
}

% ===================== INTERNSHIP =====================
\section{Internships}
\cventry{Feb. 2019 -- Apr. 2019}{\textbf{Bachelor Project}}{\href{https://www.isro.gov.in/}{ISRO}}{Bengaluru, India}{}{
\begin{itemize}
    \item Designed a 1KV DC Rectifier Unit for Doppler Weather Radar systems.
    \item Worked on mission-critical power supply systems.
\end{itemize}
}

% ===================== FREELANCING =====================
\section{Freelancing}

\cventry{Apr. 2023 -- Jul. 2023}{\textbf{Flutter Developer}}{\href{https://imcls.org/}{IMCLS}}{Remote}{}{
\begin{itemize}
    \item Built a Flutter-based storybook e-reader application for the Idu Mishmi language.
\end{itemize}
}

\cventry{Sep. 2021 -- Nov. 2021}{\textbf{Data Curator}}{\href{https://xri.institute/}{XRI Institute}}{Remote}{}{
\begin{itemize}
    \item Curated and annotated datasets for low-resource language ecosystems.
\end{itemize}
}

% ===================== PROJECTS =====================
\section{Personal Projects}

\cventry{}{Flutter Developer}{\href{https://play.google.com/store/apps/details?id=imcls.dictionary.demo_flutter}{Mishmi (Idu) Dictionary}}{}{}{
\begin{itemize}
    \item Developed UI components and offline audio features for a Flutter dictionary app.
\end{itemize}
}

\cventry{}{Frontend Developer}{\href{https://projectvani.org/about/}{VANI Project}}{}{}{
\begin{itemize}
    \item Implemented responsive static site themes using Jekyll.
\end{itemize}
}

% ===================== SKILLS =====================
\section{Skills}
\begin{itemize}
    \item \textbf{Mobile Development:} Flutter, Dart, Android, iOS
    \item \textbf{Architecture \& State Management:} Clean Architecture, MVVM, Riverpod, Stacked
    \item \textbf{Web Development:} ReactJS, JavaScript, Bootstrap, Jekyll
    \item \textbf{Backend \& APIs:} Firebase (Auth, Firestore, Storage), Appwrite, REST APIs
    \item \textbf{Databases:} Firestore, MySQL, SQLite, Drift
    \item \textbf{DevOps \& Deployment:} CI/CD (GitHub Actions), Docker, AWS, Play Store, App Store
    \item \textbf{Tools \& Practices:} Git, Jira, Agile/Scrum, Performance Optimization
\end{itemize}

% ===================== CERTIFICATIONS =====================
\section{Certifications}
\begin{itemize}
    \item Flutter Foundations Course — Andrea Bizzotto (2022)
    \item Complete Dart Language Guide — Andrea Bizzotto (2022)
\end{itemize}

\end{document}
